Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 paper.tex
fix abstract a little

%% Abstract section.
\abstract{ Consider the emerging role of data science teams embedded in
  larger organizations. Individual analysts work on loosely related problems,
  and must share their findings with each other and the organization at large,
  moving results from exploratory data analyses (EDA)
  into automated visualizations, diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, these environments often assume a single-developer perspective,
  while data scientist teams would get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a system that supports the requirements of
  collaborative data analysis, visualization and web deployment.
  The biggest deployment of RCloud has been in active use for more than a year,
  and has about fifty active users. We report on interviews with some of these users, and
  discuss the design decisions, tradeoffs and limitations, comparing RCloud
  to other current proposals.
} % end of abstract

>>>>

%% Abstract section.
\abstract{ Consider the emerging role of data science teams embedded in
  larger organizations. Individual analysts work on loosely related problems,
  and must share their findings with each other and the organization at large,
  moving results from exploratory data analyses (EDA)
  into automated visualizations, diagnostics and reports deployed for wider consumption.
  There are two problems with the current
  practice. First, there are gaps in this workflow: EDA is performed
  with one set of tools, and automated reports and deployments with another.
  Second, these environments often assume a single-developer perspective,
  while data scientist teams could get much benefit from easier sharing
  of scripts and data feeds, experiments, annotations, and automated
  recommendations, which are well beyond what traditional version control
  systems provide. We contribute and justify the following three
  requirements for systems built to support current data science teams
  and users: \emph{technology transfer}, \emph{coexistence}, and
  \emph{discoverability}. In addition, we contribute the design and
  implementation of RCloud, a system that supports the requirements of
  collaborative data analysis, visualization and web deployment.
  The biggest deployment of RCloud has been in active use for more than two years,
  and has about fifty active users. We report on interviews with some of these users, and
  discuss the design decisions, tradeoffs and limitations, comparing RCloud
  to other current proposals.
} % end of abstract
